Social Feedback For Robotic Collaboration

### 2016-05-17 paper.tex
updated observation function

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

@@

\graphicspath{{./resources/}}

\begin{document}

@@

@@

\begin{figure*}
	\begin{center}
		\begin{tabular}{r l}
			\hline
			Variable & Explanation\\
			\hline
			$s = \langle \iota, \beta, \Iota \rangle$ & A single state, defined by a tuple \\
			$\Iota$ & The set of all objects \\
			$\iota \in \Iota$ & The object desired by the human \\
			$\beta$ & A distribution over $\Iota$. $\beta_t(i_t) = p(i_t | a_{1:t-1})$ \\
			$i = \langle$name, vocab, location$\rangle$ & An object, defined by a name, vocabulary, and location \\
			$a$ & A robot action, \texttt{pick(i)}, \texttt{look(x)}, \texttt{point(x)}, or \texttt{say(x)}, observed by human  \\
			$o = \langle l, g \rangle$ & An observation received by the robot, generated by the human.  \\
			$l$ & A string of language.  \\
			$g$ & A pointing gesture.  \\
			$L$ & An indicator variable that is 1 if language is observed.  \\
			$G$ & An indicator variable that is 1 if gesture is observed.  \\
			$c_L$ & A constant that describes the probability of observing language.  \\
			$c_G$ & A constant that describes the probability of observing gesture.  \\
			$\alpha$ & A smoothing parameter for the unigram model.  \\
			$p(a_t | i_{t+1})$ & A reverse observation function \\
			$A_t$ & A diagonal matrix describing the reverse observation function $p(a_t | i_{t+1})$ for all values of $i_{t+1}$ \\
			$T$ & A matrix describing all transition probabilities $p(\iota_{t+1}|\iota_{t})$ \\
			\hline
		\end{tabular}
		\caption{Table of Variables}
		\label{fig:vars}
	\end{center}
\end{figure*}

@@

We will use the base-level observation function defined above to define a posterior observation function that considers how the base-level observation function will affect the robot's belief. Specifically, the human chooses an action proportional to the probability that the robot will hand them the desired object $\iota$ if the human had chosen that action. The robot receives this action as an observation.

\begin{align*}
p(o|s) = p(o|\iota, \beta) &\triangleq \eta p(\iota|o) \\
&= \eta \frac{p(o|\iota) p(\iota)}{\sum_{\iota^\prime} p(o|\iota^\prime)p(\iota^\prime)} 
\end{align*}

@@

@@

\begin{align*}
	p&(o|s) = \eta p(l|s) p(g|s)  \\
	&= \eta p(L|s) \left[ \frac{p(l|\iota) \beta(\iota)}{\sum_{\iota^\prime} p(l|\iota^\prime)\beta(\iota^\prime)} \right] ^ L \cdot p(G|s) \left[ \frac{p(g|\iota) \beta(\iota)}{\sum_{\iota^\prime} p(g|\iota^\prime)\beta(\iota^\prime)} \right]^G
\end{align*}

@@

To evaluate the performance of our model, we run simulated trials with two different domains: first with a toy domain, and second with the full social feedback domain. 
\subsubsection{Toy Domain Results}

The toy domain is a simplified version of the full social feedback domain. Objects are represented by binary string bits of length 3, and observations tell the robot that a particular bit has some value. There is no noise in observations. The agent can take \texttt{wait} and \texttt{pick} actions in the non-social trials, and in the social trials, can take non-social actions as well as \texttt{inform(x, y)} actions, which represent informing the human that the robot believes that the $x$th digit has value $y$.

>>>>

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}
\newcommand{\exwnote}[1]{\textcolor{orange}{\textbf{EXW: #1}}}

@@

\graphicspath{{./resources/}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\begin{document}

@@

\exwnote{The related works are a little out of date; they focus more on multimodal interpretation, even though this paper is more about modeling and action generation now}

@@

\begin{figure*}
	\begin{center}
		\begin{tabular}{r l}
			\hline
			Variable & Explanation\\
			\hline
			$s = \langle \iota, \beta, \Iota \rangle$ & A single state, defined by a tuple \\
			$\Iota$ & The set of all objects \\
			$\iota \in \Iota$ & The object desired by the human \\
			$\beta$ & A distribution over $\Iota$. $\beta_t(i_t) = p(i_t | a_{1:t-1})$ \\
			$i = \langle$name, vocab, location$\rangle$ & An object, defined by a name, vocabulary, and location \\
			$a$ & A robot action, \texttt{pick(i)}, \texttt{look(x)}, \texttt{point(x)}, or \texttt{say(x)}, observed by human  \\
			$o = \langle l, g \rangle$ & An observation received by the robot, generated by the human.  \\
			$l$ & A string of language.  \\
			$g$ & A pointing gesture.  \\
			$\epsilon$ & The probability of picking a non-optimal observation. \\
			$L$ & An indicator variable that is 1 if language is observed.  \\
			$G$ & An indicator variable that is 1 if gesture is observed.  \\
			$c_L$ & A constant that describes the probability of observing language.  \\
			$c_G$ & A constant that describes the probability of observing gesture.  \\
			$\alpha$ & A smoothing parameter for the unigram model.  \\
			$p(a_t | i_{t+1})$ & A reverse observation function \\
			$A_t$ & A diagonal matrix describing the reverse observation function $p(a_t | i_{t+1})$ for all values of $i_{t+1}$ \\
			$T$ & A matrix describing all transition probabilities $p(\iota_{t+1}|\iota_{t})$ \\
			\hline
		\end{tabular}
		\caption{Table of Variables}
		\label{fig:vars}
	\end{center}
\end{figure*}

@@

We will use the base-level observation function defined above to define a posterior observation function that considers how the base-level observation function will affect the robot's belief. Specifically, because the human is a rational agent, they will choose to generate an observation that has the greatest probability of the robot handing them their desired object $\iota$.

\begin{equation*} 
	p(o | \iota, \beta) = \begin{cases}
		1 & \text{if } o = \argmax_o p(\iota|o) \\
		0 & \text{otherwise}
	\end{cases}
\end{equation*}

To calculate $p(\iota|o)$, we can use Bayes rule:

\begin{align*}
p(\iota|o) &= \eta \frac{p(o|\iota) p(\iota)}{\sum_{\iota^\prime} p(o|\iota^\prime)p(\iota^\prime)} 
\end{align*}

@@

To account for suboptimal behavior and avoid irregularities in our observation function, we soften our assumptions of optimality such that $1-\epsilon$ fraction of the time, the human chooses the optimal action. With probability $\epsilon$ they pick acccording to the base-level observation function described above.

\begin{equation*} 
	p(o | \iota, \beta) = \begin{cases}
		(1-\epsilon) + \epsilon p(o|\iota) & \text{if } o = \argmax_o p(\iota|o) \\
		\epsilon p(o|\iota) & \text{otherwise}
	\end{cases}
\end{equation*}

@@

\begin{align*}
	p&(o|s) = \eta p(l|s) p(g|s)  \\
	 &= \eta p(L|s) p(l|\iota,\beta) ^ L \cdot p(G|s) p(g|\iota,\beta)^G
\end{align*}

@@
